% bib.tex

@article{nueda2022lpda,
  doi       = {10.1371/journal.pone.0270403},
  author    = {Nueda, María J. AND Gandía, Carmen AND Molina, Mariola D.},
  journal   = {PLOS ONE},
  publisher = {Public Library of Science},
  title     = {LPDA: A new classification method based on linear programming},
  year      = {2022},
  month     = {07},
  volume    = {17},
  url       = {https://doi.org/10.1371/journal.pone.0270403},
  pages     = {1-13},
  abstract  = {The search of separation hyperplanes is an efficient way to find rules with classification purposes. This paper presents an alternative mathematical programming formulation to existing methods to find a discriminant hyperplane. The hyperplane H is found by minimizing the sum of all the distances to the area assigned to the group each individual belongs to. It results in a convex optimization problem for which we find an equivalent linear programming problem. We demonstrate that H exists when the centroids of the two groups are not equal. The method is effective dealing with low and high dimensional data where reduction of the dimension is proposed to avoid overfitting problems. We show the performance of this approach with different data sets and comparisons with other classifications methods. The method is called LPDA and it is implemented in a R package available in https://github.com/mjnueda/lpda.},
  number    = {7},
}

@online{maxwell,
  title   = {Título do Documento no Maxwell},
  author  = {Autor do Documento},
  year    = {Ano do Documento},
  url     = {https://www.maxwell.vrac.puc-rio.br/9758/9758_3.PDF},
}

@online{kaggle,
  title   = {Heart Disease Dataset on Kaggle},
  url     = {https://www.kaggle.com/datasets/yasserh/heart-disease-dataset/data},
}

@online{pandas-docs,
  title   = {Pandas Documentation},
  url     = {https://pandas.pydata.org/docs/},
}

@online{scikit-learn-docs,
  title   = {Scikit-learn Documentation},
  url     = {https://scikit-learn.org/stable/},
}

@online{numpy-docs,
  title   = {NumPy Documentation},
  url     = {https://numpy.org/doc/},
}

@online{pulp-docs,
  title   = {Pulp Documentation},
  url     = {https://coin-or.github.io/pulp/CaseStudies/index.html},
}

@online{fastapi-docs,
  title   = {FastAPI Documentation},
  url     = {https://fastapi.tiangolo.com/},
}
